\section{appendix}

\subsection{On-issue yearly result: MERS}
\begin{enumerate}
  \item \textbf{2015.01.} Chaebol scions promoted to executives at young age
  \item \textbf{2015.02.} Umbrella union set to launch general strike in April
  \item \textbf{2015.03.} Park calls for compromise on labor, pension reforms
  \item \textbf{2015.04.} Rift prevents closure on ferry disaster
  \item \textbf{2015.05.} Presidential office blames parties for failed pension bill
  \item \textbf{2015.06.} S. Korea confirms 3 more MERS cases, total rises to 18
  \item \textbf{2015.07.} S. Korea reports no new MERS cases for 17th day
  \item \textbf{2015.08.} Park gives appointment letter to new health minister
  \item \textbf{2015.09.} Moon stakes leadership on party reform
  \item \textbf{2015.10.} 61 isolated after last MERS patient rediagnosed
  \item \textbf{2015.11.} Rival parties split over violence at protest rally
  \item \textbf{2015.12.} Police to ban another massive rally
\end{enumerate}

\subsection{On-issue yearly result: President Park's Scandal}
\begin{enumerate}
  \item \textbf{2016.01.} Lawmaker gets 16-month jail term for receiving illegal political
  \item \textbf{2016.02.} Park fills spy agency's key posts with North Korea experts
  \item \textbf{2016.03.} Executive of national swimming body arrested over alleged embezzlement
  \item \textbf{2016.04.} Ex-chief of umbrella labor union indicted over alleged illegal rallies
  \item \textbf{2016.05.} Former senior prosecutor summoned over lobbying scandal
  \item \textbf{2016.06.} Former senior prosecutor arrested for lobbying scandal
  \item \textbf{2016.07.} CJ Group chief undergoes surgery to remove lung tumor
  \item \textbf{2016.08.} Police clear Maestro Chung of embezzlement allegations
  \item \textbf{2016.09.} Cheong Wa Dae denies claims of top aide's illicit fundraising
  \item \textbf{2016.10.} Choi faces probe over influence-peddling scandal
  \item \textbf{2016.11.} Presidential office says Park will follow whatever decision parliament makes on her fate
  \item \textbf{2016.12.} Park Geun-hye impeachment explained
\end{enumerate}

\subsection{Off-issue result: MERS}
\begin{enumerate}
    \item \textbf{event 0}
    \begin{enumerate}
        \item[\textbf{who}] Korean Air
        \item[\textbf{what}] heiress gets 1 year
        \item[\textbf{when}] Thursday
        \item[\textbf{where}] Seoul
        \item[\textbf{why}] Korean Air
        \item[\textbf{how}] , former vice president of Korean Air , to one
    \end{enumerate}

    \item \textbf{event 1}
        \begin{enumerate}
        \item[\textbf{who}] President Park
        \item[\textbf{what}] welcomes labor reform deal
        \item[\textbf{when}] Tuesday
        \item[\textbf{where}] unknown
        \item[\textbf{why}] President Park Geun-hye on Tuesday
        \item[\textbf{how}] “ tough ” decision to compromise on reform measures that
        \end{enumerate}
\item \textbf{	event		2	}								
\begin{enumerate}												
\item[\textbf{	who	}]	S.	Korea								
\item[\textbf{	what	}]	reports	no	new	MERS	cases					
\item[\textbf{	when	}]	the	day	before							
\item[\textbf{	where	}]	S.	Korea								
\item[\textbf{	why	}]	S.	Korea								
\item[\textbf{	how	}]	no	new	MERS	cases	for	14th	day	.		
\end{enumerate}												
\item \textbf{	event		3	}								
\begin{enumerate}												
\item[\textbf{	who	}]	Minimum	wage								
\item[\textbf{	what	}]	declared	despite	resistance							
\item[\textbf{	when	}]	Wednesday									
\item[\textbf{	where	}]	South	Korea								
\item[\textbf{	why	}]	Minimum	wage								
\item[\textbf{	how	}]	The	South	Korean	government	Wednesday	announced	next	year	’s	minimum
\end{enumerate}												
\item \textbf{	event		4	}								
\begin{enumerate}												
\item[\textbf{	who	}]	the	chief	of	the	Korea	Confederation	of	Trade	Unions	
\item[\textbf{	what	}]	walked	out	of	the	temple					
\item[\textbf{	when	}]	11:20	a.m.								
\item[\textbf{	where	}]	Seoul									
\item[\textbf{	why	}]	police									
\item[\textbf{	how	}]	Unions	voluntarily	walked	out	of	the	temple	in	central	Seoul
\end{enumerate}												
\end{enumerate}
\subsection{Off-issue result: President Park's Scandal}

\begin{enumerate}
        \item \textbf{	event		0	}
\begin{enumerate}
\item[\textbf{	who	}]	she
\item[\textbf{	what	}]	repeatedly	rejected	to	appear	at	a	parliamentary	hearing.Members
\item[\textbf{	when	}]	Monday
\item[\textbf{	where	}]	Seoul
\item[\textbf{	why	}]	Lawmakers
\item[\textbf{	how	}]	she	repeatedly	rejected	to	appear	at	a	parliamentary	hearing.Members	of
\end{enumerate}
\item \textbf{	event		1	}
\begin{enumerate}
\item[\textbf{	who	}]	Independent	counsel	Park	Young-soo
\item[\textbf{	what	}]	faces	the	daunting	task
\item[\textbf{	when	}]	Dec.	11
\item[\textbf{	where	}]	Mir
\item[\textbf{	why	}]	They
\item[\textbf{	how	}]	Can	independent	counsel	untangle	Choi	scandal	?
\end{enumerate}
\item \textbf{	event		2	}
\begin{enumerate}
\item[\textbf{	who	}]	President	Park	Geun-hye
\item[\textbf{	what	}]	is	impeached
\item[\textbf{	when	}]	Saturday
\item[\textbf{	where	}]	Gwanghwamun	Square
\item[\textbf{	why	}]	because	of	the	people	around	me	.	”
\item[\textbf{	how	}]	only	halfway	through	‘	.
\end{enumerate}
\item \textbf{	event		3	}
\begin{enumerate}
\item[\textbf{	who	}]	A	formal	arrest	warrant
\item[\textbf{	what	}]	has	been	issued	Thursday
\item[\textbf{	when	}]	Thursday
\item[\textbf{	where	}]	Grand	Korea
\item[\textbf{	why	}]	Choi
\item[\textbf{	how	}]	’s	longtime	confidante	,	accused	of	collaborating	with	a	presidential
\end{enumerate}
\item \textbf{	event		4	}
\begin{enumerate}
\item[\textbf{	who	}]	Office
\item[\textbf{	what	}]	give	the	person
\item[\textbf{	when	}]	7:30	a.m.
\item[\textbf{	where	}]	Seoul
\item[\textbf{	why	}]	Choi	Soon-sil	,	the	mysterious	woman	accused	of	interfering	in	state	affairs	using	her	decades-long	relationship	with	President	Park	Geun-hye
\item[\textbf{	how	}]	Choi	Soon-sil	returns	;	Blue	House	‘	raid	’	by
\end{enumerate}
\item \textbf{	event		5	}
\begin{enumerate}
\item[\textbf{	who	}]	a	special	inspector
\item[\textbf{	what	}]	can	face	a	jail	term
\item[\textbf{	when	}]	Monday
\item[\textbf{	where	}]	Seoul
\item[\textbf{	why	}]	a	special	inspector
\item[\textbf{	how	}]	Special	inspector	Lee	Seok-su	,	who	had	been	tasked	with
\end{enumerate}
\end{enumerate}

